The Atala PRISM Protocol

### 2022-12-17 prism-backend/research/prism-protocol/did_atala.tex
Better defined PKI functionality.

\section{DIDs in Atala PRISM}
\label{sec:did-atala}

In this section we first give an ideal functionality for Public-Key
Infrastructures built atop of DIDs \IdealGPKIDID, and subsequently describe
Atala PRISM DID method \RealPKIDIDAtala, which is a protocol realizing
\IdealGPKIDID.
%
Before doing so, we introduce some base ideal functionalities upon which we
rely for \RealPKIDIDAtala. Namely, a simplified notion of append-only bulletin
boards, and digital signatures.

\subsection{Global Functionality \IdealGPKIDID}

\subsection{The \RealPKIDIDAtala Construction}

We next define the Atala PRISM DID method, following the interfaces defined for
\IdealGPKIDID. We begin by describing the types of keys supported in Atala
PRISM, and then specify how sets of such keys can be managed through DIDs in
Atala.

@@

\paragraph{$\P_{Atala}$ policy.} %
Before proceeding with the specififying the DID operations in Atala, we define
its policy on the keys' labels and types.

>>>>

\section{Atala PRISM's \RealPKIDIDAtala: A DID-based PKI}
\label{sec:did-atala}

In this section we first describe Atala PRISM DID method \RealPKIDIDAtala, and
prove that it realizes \IdealGPKIDID.
%
We begin by describing the types of keys supported in Atala PRISM, and then
specify how sets of such keys can be managed through the previously introduced
dictionaries in \IdealGPKIDID.

@@

\paragraph{$\P_{Atala}$ policy.} %
Before proceeding with the specififying the DID operations in Atala, we define
its policy on the keys' labels and types.
\todo{This needs to take into account the caller, and the previous state of the
  PKI list.}
